Supplementary Information for RVD2: An ultra-sensitive variant detection model for low-depth heterogeneous next-generation sequencing data

### 2014-03-18 doc/bioinformatics2014/supplementary_info.tex
Finished manuscript, supplementary information and review reply.

\documentclass[11pt,reqno]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{algorithm, algorithmic}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage[skip=2pt,font=scriptsize]{caption}
%\usepackage{epstopdf}
%\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\newcommand{\RR}{I\!\!R} %real numbers
\DeclareMathOperator{\diag}{diag}

@@

@@

%%%%%%%%%%%%%%%%%
% Appendix E: Parameter Settings for Variant Calling Algorithms
%%%%%%%%%%%%%%%%%
\section{Parameter settings for other variant calling algorithms}
\paragraph{\textbf{Samtools}}We used samtools (v0.1.19) function mpileup to call variants and bcftools to save the result in standard VCF files. In mpileup, we set the -d option sufficiently high at $10^6$ to avoid truncating read deapth. Option -u was enabled to make sure the output bcf files were uncompressed.

>>>>

\documentclass[11pt,reqno]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{algorithm, algorithmic}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{subfig}
\usepackage{enumitem}
\usepackage[skip=2pt,font=scriptsize]{caption}
\newcommand{\RR}{I\!\!R} %real numbers
%\usepackage{epstopdf}
%\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\DeclareMathOperator{\diag}{diag}

@@

%%%%%%%%%%%%%%%%%%%
% Appendix A: An simulation example to illustate the idea of proposal graphical model and v.
%%%%%%%%%%%%%%%%%%%
\section{An simulation example to illustrate the proposal graphical model and generative process.}\label{sec:appendix_example}

\begin{figure}[!bpth]
    \centering
    \subfloat[\label{fig:brca_MAF:a}]{{\includegraphics[width=0.2\textwidth]{pdf_figs/RVD2_model.pdf} }}%
    \quad
    \quad
    \subfloat[ \label{fig:brca_MAF:b}]{{\includegraphics[width=0.7\textwidth]{pdf_figs/GMexample.pdf} }}%
    \caption{(A) RVD2 Graphical Model.(B) An simulation example to illustrate the proposal graphical model and generative process. A generative process is to generate randomly observable data following your generative model, which is the reverse process of doing inference from the actual data. Here we want to generate a simulation sample with 3 replicates, and each replicate is a 5bp long sequence. Therefore, we have $ J = 5, N=3. $ The numbers in orange are known, including $\mu_0 \in \RR^{1 \times 1}$, $M_0 \in \RR^{1 \times 1}$, $M \in \RR^{5 \times 1}$, $n \in \RR^{5 \times 3}$. (1) We sample local error rate $\mu \in \RR^{5 \times 1}$ by drawing random numbers $\mu_j \thicksim \text{Beta}(\mu_0, M_0)$; (2) and then use $\mu $ and $ M $ to sample $\theta \in \RR^{5 \times 3}$ by drawing random samples $\theta_{ji} \thicksim \text{Beta}(\mu_j, M_j)$; (3) finally we use $\theta \in \RR^{5 \times 3}$ and $n \in \RR^{5 \times 3}$ to sample $r \in \RR^{5 \times 3}$ by drawing random numbers $r_{ji} \thicksim \text{Binomial}(\theta_{ji}, n_{ji})$. In actual practice, non-reference read counts $ r $ and coverage $ n $ are the data we use to do inference.} 
    \label{fig:brca_MAF}%
\end{figure}

@@

%%%%%%%%%%%%%%%%%
% Appendix E: Parameter Settings for Variant Calling Algorithms
%%%%%%%%%%%%%%%%%
\newpage
\section{Parameter settings for other variant calling algorithms}
\paragraph{\textbf{Samtools}}We used samtools (v0.1.19) function mpileup to call variants and bcftools to save the result in standard VCF files. In mpileup, we set the -d option sufficiently high at $10^6$ to avoid truncating read deapth. Option -u was enabled to make sure the output bcf files were uncompressed.
